### 2023-10-05 doc/_hierarchical_replicates_results.qmd
implement Madhav's comments

Hierarchical models present a middle ground between these extremes. First,
hierarchical models rely on the definition of so-called *hyper-parameters*, that
capture the parametric inference we are interested in---for this inference
problem, we have a hyper-fitness value $\theta^{(m)}$ for each non-neutral
barcode. Second, each experiment draws randomly from the distribution of this
hyper-parameter, allowing for subtle variability between experiments to be
accounted for---in the present inference pipeline, each experimental replicate
gets assigned a *local* fitness value $s^{(m)}_i$, where the extra sub-index
indicates the $i$-th experimental replicate. For our hierarchical model, these
local fitness values interact via the common dependency on the global
hyper-fitness value. As schematized in @fig-04(A), this interaction runs both
ways. First, the data from one experimental replicate
($\underline{\underline{R}}^M_k$ in the diagram) informs all local fitness
values via the global hyper-fitness (upper panel in @fig-04(A)). Second, the
local fitness value is informed by the data from all experimental replicates via
the same global hyper-fitness parameter (lower panel in @fig-04(A)).

>>>>

Hierarchical models present a middle ground between these extremes. First,
hierarchical models rely on the definition of so-called *hyper-parameters*, that
capture the parametric inference we are interested in---for this inference
problem, we have a hyper-fitness value $\theta^{(m)}$ for each non-neutral
barcode. Second, each experiment draws randomly from the distribution of this
hyper-parameter, allowing for subtle variability between experiments to be
accounted for---in the present inference pipeline, each experimental replicate
gets assigned a *local* fitness value $s^{(m)}_i$, where the extra sub-index
indicates the $i$-th experimental replicate. Conceptually, we can think of the
local fitness for replicate $i$ as being sampled from a distribution that
depends on the value of the global hyper-fitness value, i.e., $s^{(m)}_i \sim
\pi_{\theta^{(m)}}$, where the subindex $\theta^{(m)}$ indicates the
distribution's parametric dependence on the hyper-fitness value. This way of
interpreting the connection between the distribution $\pi_{\theta^{(m)}}$ and
the local fitness implies that a large replicate-to-replicate variability would
lead to a broad hyper-fitness distribution---implying a large uncertainty when
determining the parameter that characterizes the overall relative fitness. We
point the reader to @sec-hierarchical_model for the full definition of the
hierarchical model used in this section. Importantly, as schematized in
@fig-04(A), the influence between different experimental replicates runs both
ways. First, the data from one experimental replicate
($\underline{\underline{R}}^M_k$ in the diagram) informs all local fitness
values via the global hyper-fitness (upper panel in @fig-04(A)). Second, the
local fitness value is informed by the data from all experimental replicates via
the same global hyper-fitness parameter (lower panel in @fig-04(A)).
